### 2017-05-13 paper/evaluation.tex
Fixed # of untestable and piechart
update la02 specs
Fixed subjs section - 115 projects didn't compiled
consistency
Updated methodology of rq7

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
    hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support,
    \SubjectsGithubNotCompilable{} were unable to compile, and
    \SubjectsGithubNotTestable{} untestable projects\Comment{, and
    \SubjectsGithubFlaky{} projects with flaky tests}. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}

@@

\subsection{Tradeoffs}
\label{sec:rq6-tradeoffs}

This dimension assesses the impact of using distinct parallel
configurations on test flakiness (negative impact) and speedup
(positive impact).  Furthermore, note that Section~\ref{sec:rqD}
evaluated speedup in isolation, focused on projects configured to use
parallelism by default.

@@

To answer this research question, we conducted an experiment involving
the six parallel configurations from Section~\ref{sec:modes}  and the
top 10 long-running test modules from our sample set. The rationale
for this selection criteria was to maximize the chances of observing
speedup and flakiness, assuming that long-running tests also have many
tests. Indeed, we confirmed that test suites in these projects contain
at least 236 tests ($1,662.7$ in average). Also, we preferred to compare the
effect of a configuration over a single test module for projects with
multiple test modules.  Recall that large projects may contain several
test modules, and these modules may contain distinct characteristics
that could favor one configuration and not others; therefore, it would
be necessary to check each module individually for a fair comparison.
We are interested in understanding how efficiency (\ie, testing cost)
and flakiness (\ie, failing tests) are affected when we run a test
suite with different parallel configurations.  Recall that increased
resource contention obtained with parallelism can lead to concurrency
issues such as data races.  Flakiness and speedup are contradictory
forces that drive configuration selection.  We used as a \emph{control
group} (\ie, baseline) the sequential execution of each subject's
tests. Notice that for measuring flakiness, we have to consider only
tests that failed due to the concurrency in the parallel execution.
For that reason, we re-executed the tests in sequence ten times and
carefully verified that there are only passing tests in our baseline.
We considered ten as the number of re-executions based on the approach
used by Google reported in a previous work on test
flakiness~\cite{luo-etal-fse2014}.  To obtain parallel configurations,
we implemented a script that takes a subject and a configuration (\eg,
\ForkSeq{}) as inputs, and the script outputs the modified version of
the subject with the desired configuration. The workflow consists in
copying the project directory to a new directory, finding all existing
build files (\ie, \pomf{} files), and modifying all existing Maven
Surefire configurations with new values for the parameters
\CodeIn{parallel}, \CodeIn{forkCount}, and \CodeIn{threadCount} using
an XPath~\cite{xpath} library to manipulate XML documents. For
configurations with forked JVMs enabled (\ie, \ForkSeq{} and
\ForkParMeth{}), we changed the \CodeIn{forkCount} with the value
\CodeIn{1C} (\ie, one JVM per core).  To adjust the pool of threads
for parallelism within a JVM, we changed the parameter
\CodeIn{threadCount} with \Jbc{should we consider 2 as it is the
number of native threads per core OR 6 as it represents 3 Cores * 2
native threads?}.  To run the subjects and their respective variations
(\ie, the modified versions according to the parallelism
configuration), we used a similar approach as described in

Figure~\ref{fig:mvn-execution} except that we added a timeout of one
hour to run the tests. We used the \CodeIn{timeout}
command~\cite{timeout-cmd} to monitor the execution, and we configured
the command to dispatch a \emph{kill} signal if the test execution
exceeds the time limit. We imposed this time constraint to avoid
hanging indefinitely the experiment execution due to some thread
contention that may occur (\eg, deadlock). Finally, we saved each
execution log and XML test reports generated by Maven to collect the
execution time, the number of failing tests, and for reference to
analyze and diagnose outliers in our results. For efficiency, we
reported the speedup (\ie, $\Uparrow_\text{speed} = T_{\text{s}} /
T_{\text{p}}$) in average, and for flakiness, we reported the rate of
failing tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$) in
average.  Figure~\ref{tab:rq6-table} summarizes the obtained results
ordered by the time cost (\ie, $T_\text{cost}$). \Fix{Remember to
explain efficiency cutoff, JVM crashes and timeout}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
    hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support,
    \SubjectsGithubNotCompilable{} uncompilable projects, and
    \SubjectsGithubNotTestable{} untestable projects\Comment{, and
    \SubjectsGithubFlaky{} projects with flaky tests}. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}

@@

\subsection{Tradeoffs}
\label{sec:rq6-tradeoffs}
\Jbc{Check $\rightarrow$}
This dimension assesses the impact of using distinct parallel
configurations on test flakiness (negative impact) and speedup We are
interested in understanding how efficiency (\ie, testing cost) and
flakiness (\ie, failing tests) are affected when we run a test suite
with different parallel configurations.  Recall that increased
resource contention obtained with parallelism can lead to concurrency
issues such as data races.  Flakiness and speedup are contradictory
forces that drive configuration selection.  (positive impact).
Furthermore, note that Section~\ref{sec:rqD} evaluated speedup in
isolation, focused on projects configured to use parallelism by
default.

@@

To answer this research question, we conducted an experiment involving
the six parallel configurations from Section~\ref{sec:modes}, and we
randomly selected 10 subjects from the medium and long groups (\ie,
tests suites that ran in at least one minute) identified in
\numRQFeasibilityOne{}. \Jbc{Is this legit/acceptable/convincing?
$\rightarrow$}The rationale for this criteria was to maximize the
diversity of domains from the subjects, assuming these subjects have
test suites with different characteristics (\eg, architectural design
and rate of cpu/io-bound operations).
\Comment{
    The rationale for this selection criteria was to maximize the chances
    of observing speedup and flakiness, assuming that long-running tests
    also have many tests. Indeed, we confirmed that test suites in these
    projects contain at least 236 tests ($1,662.7$ in average).
}
To compare flakiness and efficiency, we used the sequential execution
of each subject's test suite as the \emph{control group} (\ie,
baseline). Notice that with parallelism enabled, the number of failing
tests may vary on different runs due to the non-deterministic
scheduling of threads and processes.  For that reason, we re-executed
the experiment and computed the average speedup and flakiness on each
scenario. 
In a first attempt of this experiment, we considered using Maven to
run the subjects on the different parallel configurations. However, we
noticed that some executions using parallelism within a JVM did not
reflect the desired behavior although we carefully verified the
library versions from the subjects tested to avoid compatibility
issues.
To make the experiment viable and obtain the parallel configurations,
we implemented a script and a JUnit runner to emulate the effect of
parallel configurations from Maven Surefire.
Our script takes a list o tests classes to run as an input and outputs
the results (\ie, number of test methods, failures, skips, and elapsed
time) for each parallel configuration. Initially, we use an existing
Maven log to identify the test classes to run, and we use the Maven
dependency plugin~\cite{maven-dep} to build the project's classpath with
the command \CodeIn{mvn dependency:build-classpath}. Once we have the
classpath and the tests to run, we invoke our JUnit runner that runs
the test classes with different parallel configurations at once. For
the sequential execution, we ivonke the default JUnit test runner. For
parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
runner with ParallelComputer~\cite{junit-parallel} that internally uses a pool of
threads with cache to run test classes and methods. For the
configurations with forked JVMs (\ie, \ForkSeq{} and \ForkParMeth{}),
we have a queue of test classes and a pool of three threads that
``consumes'' the next test class and spawns a JVM to run it.
Recall that in our setup (see Section~\ref{sec:setup}), we limited our
kernel to use only three cores and reserved one for OS-related
processes.
To verify that our approach satisfies the purpose of this experiment,
we executed some subjects on Maven and compared the performance with
our artifacts and observed nonsignificant differences (a fraction of
seconds in most cases).
\Comment{
    To obtain parallel configurations, we implemented a script that
    takes a subject and a configuration label as inputs (\eg
    \CodeIn{mapdb "c0"}), and the script outputs the modified version
    of the subject with the desired configuration. The workflow
    consists in copying the project directory to a new directory,
    finding all existing build files (\ie, \pomf{} files), and
    modifying all existing Maven Surefire configurations with new
    values for the parameters \CodeIn{parallel}, \CodeIn{forkCount},
    and \CodeIn{threadCount} using an XPath~\cite{xpath} library to
    manipulate XML documents. For configurations with forked JVMs
    enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
    \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
    core).  To adjust the pool of threads for parallelism within a
    JVM, we changed the parameter \CodeIn{threadCount} with
    \Jbc{should we consider 2 as it is the number of native threads
    per core OR 6 as it represents 3 Cores * 2 native threads?}.To run
    the subjects and their respective variations (\ie, the modified
    versions according to the parallelism configuration), we used a
    similar approach as described in Figure~\ref{fig:mvn-execution}
    except that...
}
Also, we used the \CodeIn{timeout} command~\cite{timeout-cmd} in our
scripts to monitor the execution, and we configured the command to
dispatch a \emph{kill} signal if the test execution exceeds a given
time limit. We imposed this time constraint to avoid hanging
indefinitely the experiment execution due to some thread contention
that may occur (\eg, deadlock or livelock).  Finally, we saved each
execution log and stack traces generated outputed from JUnit to
collect the execution time, the number of failing tests, and for
reference to analyze and diagnose outliers in our results.  For
efficiency, we reported the speedup (\ie, $T_{\text{s}} /
T_{\text{p}}$), and for flakiness, we reported the rate of failing
tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
subject's name. Values are reported in average \Fix{LEMBRAR DE MOSTRAR
VALORES DE DESVIO PADRAO!}.
